


\begin{longtable} {|m{0.1\textwidth}|m{0.8\textwidth}|m{0.1\textwidth}|}
\hline
\textbf{ID} & \textbf{ITEM} & \textbf{CHECK} \\
\hline
\multicolumn{2}{|l|}{ \textbf{SCIENCE} } & \\
\hline
& \textbf{CAC} & \\
\hline
& Remove the CAC wall with the D-SUB connector, if it's not removed already. & \\ \hline
& Remove the CAC wall with the D-SUB connector, if it's not removed already. & \\ \hline
S1 & Connect picarro to quick connector stem at No 10. & \\ \hline
S2 & Attach the fill gas bottle's quick connector stem to quick connector body No 1. & \\ \hline
S3 & Let the fill gas run through the AirCore at a flow rate of 40ml/min. & \\ \hline
S4 & Leave it flushing over night. & \\ \hline
S5 & Detach quick connector stem at No 1. & \\ \hline
S6 & Detach the quick connector stem at No 10. & \\ \hline
S7 & Disconnect the picarro analyser. & \\ \hline
S8 & Connect the dryer tube No 14 to No 13. & \\ \hline
S9 & Connect parts 11 to 21. & \\ \hline
S10 & Check all connections are tighten. & \\ \hline
S11 & Close the CAC's solenoid valve No 17. & \\ \hline
S12 & Connect quick connector stem No 10 to No 9. & \\ \hline
S13 & Connect No 10 with No 11. & \\ \hline
S14 & Check all connections are tighten. & \\ \hline
S15 & Put the CAC wall with the D-SUB connector back. & \\ \hline
& \textbf{AAC/MANIFOLD} & \\ \hline
S16 & Unscrew the plug from the inlet (1) and outlet tube (29). & \\ \hline
S17 & Screw in the male threaded quick connector to the inlet tube (1). & \\ \hline
S18 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's inlet tube (1). & \\ \hline
S19 & Connect a flow rate sensor close to the outlet tube (29). & \\ \hline
S20 & Open flushing valve (27). & \\ \hline
S21 & Turn central valve on so that is open to dry gas. & \\ \hline
S22 & Let the dry gas run through the AAC's manifold for 10 minutes. & \\ \hline
S23 & Close flushing valve (27) & \\ \hline
S24 & Turn central valve off so that is close to dry gas. & \\ \hline
S25 & Leave the vacuum pump and the dry gas bottle through a central valve to the AAC's inlet tube (1). & \\ \hline
& \textbf{AAC/TUBES} & \\ \hline
S26 & Connect quick connector with stem at the tube T-union of the 1st bag (33) & \\ \hline
S27 & Open 1st bag's solenoid valve in the manifold (23). & \\ \hline
S28 & Open central valve so that is open to dry gas. & \\ \hline
S29 & Let the dry gas run through the tube for 2 mins at a flow rate of 2 L/min. & \\ \hline
S30 & Attach 1st bag. & \\ \hline
S31 & Let the dry gas run through for 1 more minute. & \\ \hline
S32 & Open 2nd bag's solenoid valve in the manifold (23). & \\ \hline
S33 & Close 1st bag's solenoid valve in the manifold (23). & \\ \hline
S34 & Disconnect quick connector with stem from the T-union of the 1st bag (33). & \\ \hline
S35 & Connect quick connector with stem at the tube T-union of the 2nd bag (33). & \\ \hline
S36 & Let the dry gas run through the tube for 2 mins at a flow rate of 2 L/min. & \\ \hline
S37 & Attach the 2nd bag. & \\ \hline
S38 & Let the dry gas run through for 1 more minute. & \\ \hline
S39 & Open 3rd bag's solenoid valve in the manifold (23). & \\ \hline
S40 & Close 2nd bag's solenoid valve in the manifold (23). & \\ \hline
S41 & Disconnect quick connector with stem from the T-union of the 2nd bag (33). & \\ \hline
S42 & Connect quick connector with stem at the tube T-union of the 3rd bag (33). & \\ \hline
S43 & Let the dry gas run through the tube for 2 mins at a flow rate of 2 L/min. & \\ \hline
S44 & Attach the 3rd bag. & \\ \hline
S45 & Let the dry gas run through for 1 more minute. & \\ \hline
S46 & Open 4th bag's solenoid valve in the manifold (23). & \\ \hline
S47 & Close 3rd bag's solenoid valve in the manifold (23). & \\ \hline
S48 & Disconnect quick connector with stem from the T-union of the 3rd bag (33). & \\ \hline
S49 & Connect quick connector with stem at the tube T-union of the 4th bag (33). & \\ \hline
S50 & Let the dry gas run through the tube for 2 mins at a flow rate of 2 L/min. & \\ \hline
S51 & Attach the 4th bag. & \\ \hline
S52 & Let the dry gas run through for 1 more minute. & \\ \hline
S53 & Open 5th bag's solenoid valve in the manifold (23). & \\ \hline
S54 & Close 4th bag's solenoid valve in the manifold (23). & \\ \hline
S55 & Disconnect quick connector with stem from the T-union of the 4th bag (33). & \\ \hline
S56 & Connect quick connector with stem at the tube T-union of the 5th bag (33). & \\ \hline
S57 & Let the dry gas run through the tube for 2 mins at a flow rate of 2 L/min. & \\ \hline
S58 & Attach the 5th bag. & \\ \hline
S59 & Let the dry gas run through for 1 more minute. & \\ \hline
S60 & Open 6th bag's solenoid valve in the manifold (23). & \\ \hline
S61 & Close 5th bag's solenoid valve in the manifold (23). & \\ \hline
S62 & Disconnect quick connector with stem from the T-union of the 4th bag (33). & \\ \hline
S63 & Connect quick connector with stem at the tube T-union of the 5th bag (33). & \\ \hline
S64 & Let the dry gas run through the tube for 2 mins at a flow rate of 2 L/min. & \\ \hline
S65 & Attach the 6th bag. & \\ \hline
S66 & Let the dry gas run through for 1 more minute. & \\ \hline
S67 & Turn central valve off so that is close to dry gas. & \\ \hline
S68 & Close 6th bag's solenoid valve in the manifold (23). & \\ \hline
S69 & Disconnect quick connector with stem from the T-union of the 6th bag (33). & \\ \hline
S70 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's inlet tube (1). & \\ \hline
S71 & Leave the quick connector to the AAC's inlet tube (1). & \\ \hline
S72 & Leave the male threaded quick connector to the AAC's outlet tube (29). & \\ \hline
& \textbf{AAC/BAGS} & \\ \hline
S73 & Connect the vacuum pump and the dry gas bottle through a central valve to the AAC's outlet tube (29). & \\ \hline
S74 & Connect a flow rate sensor close to the central valve. (valve that controls vaccum or filling bags). & \\ \hline
S75 & Make sure the AAC's inlet tube (1) is shielded. & \\ \hline
S76 & Open 1st bag's manual valve. & \\ \hline
S77 & Open flushing valve (27). & \\ \hline
S78 & Open 1st bag's solenoid valve in the manifold (23) & \\ \hline
S79 & Open central valve so that is open to dry gas. & \\ \hline
S80 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S81 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S82 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S83 & Turn the central valve open to dry gas. & \\ \hline
S84 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S85 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S86 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S87 & Repeat steps S34 to S37 one more time. & \\ \hline
S88 & Close 1st bag's solenoid valve in the manifold (23). & \\ \hline
S89 & Open 2nd bag's manual valve. & \\ \hline
S90 & Open 2nd bag's solenoid valve in the manifold (23). & \\ \hline
S91 & Open central valve so that is open to dry gas. & \\ \hline
S92 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S93 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S94 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S95 & Turn the central valve open to dry gas. & \\ \hline
S96 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S97 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S98 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S99 & Repeat steps S46 to S49 one more time. & \\ \hline
S100 & Close 2nd bag's solenoid valve in the manifold (23). & \\ \hline
S101 & Open 3rd bag's manual valve. & \\ \hline
S102 & Open 3rd bag's solenoid valve in the manifold (23). & \\ \hline
S103 & Open central valve so that is open to dry gas. & \\ \hline
S104 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S105 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S106 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S107 & Turn the central valve open to dry gas. & \\ \hline
S108 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S109 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S110 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S111 & Repeat steps S58 to S61 one more time. & \\ \hline
S112 & Close 3rd bag's solenoid valve in the manifold (23). & \\ \hline
S113 & Open 4th bag's manual valve. & \\ \hline
S114 & Open 4th bag's solenoid valve in the manifold (23). & \\ \hline
S115 & Open central valve so that is open to dry gas. & \\ \hline
S116 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S117 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S118 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S119 & Turn the central valve open to dry gas. & \\ \hline
S120 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S121 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S122 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S123 & Repeat steps S70 to S73 one more time. Total 3 times. & \\ \hline
S124 & Close 4th bag's solenoid valve in the manifold (23). & \\ \hline
S125 & Open 5th bag's manual valve. & \\ \hline
S126 & Open 5th bag's solenoid valve in the manifold (23). & \\ \hline
S127 & Open central valve so that is open to dry gas. & \\ \hline
S128 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S129 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S130 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S131 & Turn the central valve open to dry gas. & \\ \hline
S132 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S133 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S134 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure!!! & \\ \hline
S135 & Repeat steps S82 to S85 one more time. Total 3 times. & \\ \hline
S136 & Close 5th bag's solenoid valve in the manifold (23). & \\ \hline
S137 & Open 6th bag's manual valve. & \\ \hline
S138 & Open 6th bag's solenoid valve in the manifold (23). & \\ \hline
S139 & Open central valve so that is open to dry gas. & \\ \hline
S140 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S141 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S142 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure. & \\ \hline
S143 & Turn the central valve open to dry gas. & \\ \hline
S144 & Start filling the bag with 3L of dry gas with a flow rate of 2L/min for 1.5 minutes. & \\ \hline
S145 & After 1.5 mins, when the bag is full, turn the central valve open to the vacuum , allowing the bag to empty. & \\ \hline
S146 & Empty the bag with controlled vacuum only 1-2 mbar below ambient pressure!!! & \\ \hline
S147 & Repeat steps S94 to S97 one more time. & \\ \hline
S148 & Close 6th bag's solenoid valve in the manifold (23). & \\ \hline
S149 & Close flushing valve (27). & \\ \hline
S150 & Disconnect the vacuum pump and the dry gas bottle through a central valve from the AAC's outlet tube (29). & \\ \hline
S151 & Screw in the plug to the AAC outlet tube (29). & \\ \hline



\multicolumn{2}{|l|}{  \textbf{ELECTRICAL} } & \\ \hline
E1 & Check that all (3 9-Pin, Bags, Out, CAC, and 2 15-pin, Level 1 and 2) D-subs are connected and screwed in on the PCB (hand tight, DO NOT TIGHTEN TO HARD). & \\ \hline
E2 & Check that plastic 28.8V power is connected to level 1 and 2 connectors (Red wire, plastic connector, Male on wires going to each level, female is underneath the PCB.).& \\ \hline
E3 & Check that the plastic 28.8V power cable from the PCB is secured with zip tie to one of the standoffs. & \\ \hline 
E4 & Check that power is plugged in on the PCB. & \\ \hline
E5 & Check that Ethernet is connected form PCB to wall. (should hear click) & \\ \hline
E6 & Check that outside pressure sensors are connected to the outside upper (furthest from frame) 9-pin D-sub wall connector (hand tight, DO NOT TIGHTEN TO HARD). & \\ \hline
E7 & Check that CAC is connected on the outside lower (closest to frame) 9-pin D-sub wall connector (hand tight, DO NOT TIGHTEN TOO HARD). & \\ \hline
E8 & Check that power is connected on the outside wall. & \\ \hline
E9 & Check that the Ethernet is connected on the outside wall (should hear click). & \\ \hline
E10 & Check main PCB board is secure (Locking nuts where possible and no nut for the rest).\\ \hline
E11 & Check that pressure sensors are secure on the outside (Bolted down with locking nuts). & \\ \hline
E12 & Check output voltage from DCDC's and make sure they are used equally (after diode). & \\ \hline
E13 & Verify sensors give data to ground station. & \\ \hline
E14 & Verify that all valves open and close as expected (listen and check PCB lights).& \\ \hline
E15 & Verify that heaters get warm when they are turned on (Check temp data, feel, and check lights)& \\ \hline
\multicolumn{2}{|l|}{  \textbf{SOFTWARE} } & \\ \hline
SW1 & The ground station laptop PC will need to be put in place and operational. & \\ \hline
SW2 & The correct version of the onboard software have been uploaded to the OBC. & \\ \hline
SW3 & The communication through E-link with the experiment shall be tested. & \\ \hline
SW4 & Verify that the data from sensors are  realistic. & \\ \hline
SW5 & The air sampling itinerary is checked. & \\ \hline
SW6 & SD card contents are checked. & \\ \hline
\multicolumn{2}{|l|}{ \textbf{MECHANICAL} } & \\
\hline
M1 & Check that the frame structure is properly fixed. & \\
\hline
M2 & Check that the handles of both boxes are properly fixed. & \\
\hline
& \textbf{AAC BOX} & \\
\hline
M3 & Check that The Brain is properly attached to the structure of the AAC Box. & \\
\hline
M4 & Check that all the pneumatic connections are set (interfaces, valves, bags): use the manufactured tool for this matter. & \\
\hline
M5 & Check that the bags valve are open. & \\
\hline
M6 & Check that the bags are properly fixed with the circular bar. & \\
\hline
M7 & Check that the electronic interfaces panel is properly fixed to the top wall. & \\
\hline
M8 & Close all the open walls and check that they are all properly fixed and closed. & \\
\hline
M9 & Unscrew the plugs from the inlet and the outlet tube. & \\
\hline
& \textbf{CAC BOX} & \\
\hline
M10 & Check that the AirCore is properly placed. & \\
\hline
M11 & Check that all the pneumatic connections are set (interfaces, valves) & \\
\hline
M12 & Close all the open walls and check that they are all properly fixed and closed. & \\
\hline
M13 & Unscrew the plug from the inlet/outlet tube. & \\
\hline
& \textbf{GONDOLA} & \\
\hline
M14 &  Attach both boxes one to the other. & \\
\hline
M15 & Introduce both boxes inside the gondola. & \\
\hline
M16 & Check that the experiment box is fixed to the gondola rails (10 anchor points). & \\
\hline
M17 & Check that the electronic connectors are properly fixed to both electronic panels (D-sub, power, E-link) & \\
\hline


\end{longtable}
