\subsection{Input for the Campaign / Flight Requirements Plans}


\subsubsection{Dimensions and Mass}
\label{sec:dim-mass}

The data shown in Table \ref{tab:dim-mass-tab} below is based on the design presented in Section \ref{Mechanical_Design}. %The mass for the electronics is estimated to be 1.5 kg.  

\input{6-launch-campaign-preparation/tables/dimenstionsmasstable.tex}

\subsubsection{Safety Risks}
Table \ref{tab:safrisk} contains the risks of all stages of the whole campaign and project.
\input{6-launch-campaign-preparation/tables/safety-risk.tex}

\subsubsection{Electrical Interfaces}

Please refer to Table \ref{tab:electrical-interface-table} for details on the electrical interfaces with the gondola.

\input{6-launch-campaign-preparation/tables/electricalinterface.tex}

\subsubsection{Launch Site Requirements}
Prior to launcch, in the case that ice has appeared on the experiment prohibiting free motion for the controller, a small electric heater fan will be needed to remove the ice.

Post launch a laptop PC will be used to send and receive data to the experiment. For this a desk and chair will be needed, along with a power outlet and ethernet cable for e-link connection.


\subsubsection{Flight Requirements}
The flight requirements for the IRISC experiment are stated below.
\begin{itemize}
	\item \textbf{Desired float altitude:} A height of >20\,km is adequate for this experiment. However, a higher altitude will improve the signal to noise ratio.
	\item \textbf{Desired float duration:} We need a floating time of at least 90 min in order to collect sufficient amount of data. A longer floating time would desirable.
	\item \textbf{Required launch time:} A partial night flight would be preferable because there is less interference with the sun and a wider range of view. However, the system will be designed to be able to function during the entire day.
\end{itemize}

\subsubsection{Accommodation Requirements}

