\section*{PREFACE} \markboth{}{}
\addcontentsline{toc}{section}{PREFACE}

The Rocket and Balloon Experiments for University Students (REXUS/BEXUS) programme is realized under a bilateral Agency Agreement between the German Aerospace Center (DLR) and the Swedish National Space Agency (SNSA). The Swedish share of the
payload has been made available to students from other European countries through a collaboration with the European Space Agency (ESA).

EuroLaunch, a cooperation between the Esrange Space Center of SSC and the Mobile Rocket Base (MORABA) of DLR, is responsible for the campaign management and operations of the launch vehicles. Experts from DLR, SSC, ZARM, and ESA provide
technical support to the student teams throughout the project.

The Student Experiment Documentation (SED) is a continuously updating document regarding the BEXUS student experiment IRISC - InfraRed Imaging of astronomical targets with a Stabilized Camera and will undergo reviews during the preliminary design review, the critical design review, the integration progress review, and final experiment report.

The goal of the IRISC experiment is to obtain images in the near infrared (NIR) spectrum from astronomical targets. Possible targets include the Andromeda Galaxy, Pinwheel Galaxy, Iris Nebula, Eagle Nebula and Starfish Cluster. The images are obtained using a highly stabilized telescope with NIR camera mounted on a BEXUS balloon. With this balloon-borne telescope most interference caused by the atmosphere is avoided-- a problem for most ground-based telescopes-- while keeping the building and operation costs low, compared to an orbital telescope. The stabilization is achieved by a gimbal-like system, this is needed to obtain high quality images while being on a moving platform. For a NIR telescope, it is also important to keep the temperature as low as possible to avoid heat-induced noise. For example, orbital telescopes are kept at only a few degrees above 0 K. IRISC wants to use a NIR camera with a higher operating temperature (closer to 273 K) that requires a relatively simple cooling system. The aim is to develop a simple astronomical research system that is affordable and readily available for integration with other future stratospheric balloon experiments. 
%The bit specific to your team goes here. Obviously remove the bit about TUBULAR and insert your own name xP
