\pagebreak
\subsection{Power System}
<<<<<<< HEAD
A 28.8V/1mA battery package can be provided by the gondola, according to the BEXUS user manual. Which should satisfy IRISC's power needs. One constraint is that the continuous maximum current is 1.8 A. Thus a buck-converter will be needed to step down the voltage, so that the power system will be able to provide the right voltages for the rest of the subsystems.  
=======
A 28.8V battery package can be provided by the gondola, according to the BEXUS user manual. One constrain is that the continuous maximum current is 1.8 A. Thus buck-converters will be needed to step down the voltage, while stepping up the current, so that the power needed will be delivered to the instrument. The voltage levels of the buck converters are: 
>>>>>>> 5987848b9c3240acbf313774946f8126c279df23

\begin{itemize}
	\item 28.8 V --> 3.3 V, with the power 1.65 W.
	\item 28.8 V --> 5 V, with power 15 W.
	\item 28.8 V --> 12 V, with power 15 W.
\end{itemize}

A schematic of the power system can be found in the appendix C.

The estimated power consumption of the components are shown in table \ref{tab: power consumption}. 
% import table of estimated power for components.
<<<<<<< HEAD
=======
\input{4-experiment-design/tables/component-power.tex}

\newpage

The BEXUS manual recommends the instrument to be prepared to have power supplies for 2 hours of testing, 2 hours on ground and for a flight time of 6 hours as a minimum. The instrument therefore needs to be in active mode for at least 8 h, because on ground the instrument will be in sleep mode. The instrument will also be in sleep mode for ascending and descending of the gondola. 

The total estimated power for the instrument:

\begin{itemize}
    \item Active mode: 38.02 W  --> 304 Wh (8h)
    \item Sleep mode: 15 W --> 45Wh (3h) 
\end{itemize}

Thus the instrument will require at least 349 Wh. The maximum power provided by the gondola will be 375 Wh, which should satisfy the instruments needs.
>>>>>>> 5987848b9c3240acbf313774946f8126c279df23




\raggedbottom
