% https://www.tablesgenerator.com/ highly recommended.

\makeatletter
\renewcommand\@makefntext[1]{\leftskip=3em\hskip-1em\@makefnmark#1}
\makeatother

\begin{longtable}[]{|m{0.05\textwidth}| m{0.41\textwidth}|m{0.11\textwidth}|m{0.11\textwidth}|m{0.11\textwidth}|m{0.11\textwidth}|}

\hline
\textbf{ID} & \textbf{Requirement text} & \textbf{Method} & \textbf{Reference} & \textbf{Status} & \textbf{Verifica-tion result} \\\hline

 F.3 & The system shall be able to find the celestial objects of interest at the location and orientation of the gondola.
& A, T & Tests: 5, 10 & A: to be done \newline T: to be done & Not verified \\\hline

  F.4 & The system shall be able to orient towards selected celestial objects of interest.
& A, T & Test: 5, 10 & A: to be done \newline T: to be done & Not verified \\\hline

  F.5 & The system shall be able to counter balance perturbations of the gondola during exposure.
& A, T & Test: 3, 4, 5, 10 & A: to be done \newline T: to be done & Not verified \\\hline

  F.6 & The camera and optics system shall be able to record the selected celestial object of interest.
& A, T & Test: 3, 4, 5, 10 & A: to be done \newline T: to be done & Not verified \\\hline




P.2 & The optics shall be cable of making pictures of 0.5-1.5 x 0.3-1\,degrees.
& R, T & Test: 1, 12 & R: to be done \newline T: to be done  & Not verified \\\hline

P.3 & The NIR camera shall make images in the range of 720-850 to 1200\,nm.
& R & Test: 1, 12 & R: to be done  & Not verified \\\hline

P.4 & The NIR camera shall have a resolution of at least 16\,MP.
& R, T& Test: 1, 12 & R: to be done \newline T: to be done & Not verified \\\hline

P.5 & The NIR camera shall be able to take pictures with an exposure time up to 30\,seconds.
& R, T & Test: 1, 12 & R: to be done \newline T: to be done & Not verified \\\hline

  P.8 & The gimbal system shall be able to stabilize the telescope towards the celestial object with an accuracy of at least 1 arcsecond during exposure.
& A, T & Test: 3, 4, 5, 10 & A: to be done \newline T: to be done & Not verified \\\hline

  P.9 & The system shall be able measure the orientation of the gondola with an accuracy of 0.5 degree.
& R, T & Test: 3, 12 & R: to be done \newline T: to be done  & Not verified \\\hline

  P.10 & The system shall be able measure the position of the gondola with an accuracy of 5 meters.
& R & Test: 12 & R: to be done & Not verified \\\hline

  P.11 & The pointing error of the guiding camera in relation to the NIR camera shall be less than 0.35 degrees.
& R & Test: 12 & R: to be done & Not verified \\\hline

  P.12 & The temperature of the NIR camera shall be held between -5 and 0\,$^\circ$C during operation.
& T & Test: 2a & T: to be done & Not verified \\\hline

  P.13 & The temperature of the NIR camera should be held between -5 and -3\,$^\circ$C during operation.
& T & Test: 2a &  T: to be done & Not verified \\\hline

  P.14 & The temperature of the rotating part shall be held between 0 and 85\,$^\circ$C.
& T & Test: 2a & R: T: to be done & Not verified \\\hline

  P.15 & The temperature of the electronics shall be held between -40 and 85\,$^\circ$C.
& T & Test: 2a & T: to be done & Not verified \\\hline



D.01 & The experiment shall be able to operate in the temperature profile of the BEXUS environment.
& T & Test: 2a & T: to be done & Not verified \\\hline

D.02 & The experiment shall be able to operate in the pressure profile of the BEXUS environment.
& T & Test: 2b  & T: to be done & Not verified \\\hline

D.03 & The experiment shall be able to operate in the vibration profile of the BEXUS environment.
& T & Tests: 10 & T: to be done & Not verified \\\hline

D.05 & The supporting structure shall not twist by more than 0.1\,degrees.
& T & Tests: 9, 10 & T: to be done & Not verified \\\hline

D.07 & The experiment shall be able to fly during the entire day.
& T & Tests: 9, 10, 11 & T: to be done & Not verified \\\hline

D.10 & The experiment shall be mounted at the side of the gondola.
& T & Tests: 9, 10 & T: to be done & Not verified \\\hline

D.11 & The experiment shall not consume more power than 250\,Wh.
& T & Tests: 9, 10 & T: to be done & Not verified \\\hline

D.13 & The mass of the experiment shall not exceed 20\,kg.
& T & Test: 7 & T: to be done & Not verified \\\hline

D.14 & The experiment shall be able to run for at least 2.5\,hours.
& T & Tests: 9, 10 & T: to be done & Not verified \\\hline

D.15 & The experiment should be able to run for at least 4\,hours.
& T & Tests: 9, 10 & T: to be done & Not verified \\\hline

D.16 & The experiment shall be able to function autonomously.
& T & Tests: 4, 9, 10 & T: to be done & Not verified \\\hline

D.17 & The data stored in the experiment shall be able to survive the landing.
& T & Test: 8, 11 & T: to be done & Not verified \\\hline

  D.18 & The images obtained shall be sent to a ground station by the E-link system with a various and adjustable data rate between 250 and 1000 kilo bits per second.
& T & Test: 6 & T: to be done & Not verified \\\hline




O.1 & The experiment shall be able to be controlled by the ground station when requested.
& T & Tests: 4, 10 & T: to be done & Not verified \\\hline

O.2 & The experiment shall rotate to a 'safe' position while descending.
& T & Tests: 4, 9, 10 & T: to be done & Not verified \\\hline

 O.3 & The telescope shall not be pointed within 27\,degrees of the sun.
& R & Tests: 11 & T: to be done & Not verified \\\hline

\caption{Verification Matrix.}
\label{tab:var-mat}
\end{longtable}
\raggedbottom