\subsection{Performance Requirements}

\begin{enumerate}[topsep=0pt,itemsep=-1ex,partopsep=1ex,parsep=1ex]
    \item[P.1] \colorbox{yellow}{\parbox{\textwidth}{\st{The gimbal system shall be able to stabilize the telescope towards the celestial object with an accuracy of at least 1 arcsecond during exposure.} \textit{Moved to req. P.8}}}
    \item[P.2] The optics shall be capable of making pictures of 0.5-1.5 x 0.3-1\,degrees.
    \item[P.3] The NIR camera shall make images in the range of 720 to 1200\,nm.
    \item[P.4] The NIR camera shall have a resolution of at least 16\,MP.
    \item[P.5] \colorbox{yellow}{\parbox{\textwidth}{The NIR camera shall be able to take pictures with an exposure time up to 30\,seconds.}}
    \item[P.6] \colorbox{yellow}{\parbox{\textwidth}{\st{The experiment shall establish the location and orientation of the gondola.} \textit{Moved to functional req F.3.}}}
    \item[P.7] \colorbox{yellow}{\parbox{\textwidth}{\st{The system shall be able to store all the obtained data on board.}}}
    \item[P.8] The gimbal system shall be able to stabilize the telescope towards the celestial object with an accuracy of at least 1 arcsecond during exposure.
    \item[P.9] \colorbox{yellow}{\parbox{\textwidth}{The system shall be able measure the orientation of the gondola with an accuracy of 0.5 degree.}}
	\item[P.10] \colorbox{yellow}{\parbox{\textwidth}{The system shall be able measure the position of the gondola with an accuracy of 5 meters.}}
	\item[P.11] \colorbox{yellow}{\parbox{\textwidth}{The pointing error of the guiding camera in relation to the NIR camera shall be less than 0.35 degrees.}}
	\item[P.12] \colorbox{yellow}{\parbox{\textwidth}{The temperature of the NIR camera shall be held between -5 and 0\,$^\circ$C during operation.}}
	\item[P.12] \colorbox{yellow}{\parbox{\textwidth}{The temperature of the NIR camera should be held between -5 and -3\,$^\circ$C during operation.}}
	\item[P.13] \colorbox{yellow}{\parbox{\textwidth}{The temperature of the rotating part shall be held between 0 and 85\,$^\circ$C.}}
	\item[P.14] \colorbox{yellow}{\parbox{\textwidth}{The temperature of the electronics shall be held between -40 and 85\,$^\circ$C.}}
\end{enumerate}
