\subsection{Design Requirements}

\begin{enumerate}
	\item[D.01] The experiment shall be able to operate in the temperature profile of the BEXUS environment.
	\item[D.02] The experiment shall be able to operate in the pressure profile of the BEXUS environment.
    \item[D.03] The experiment shall be able to operate in the vibration profile of the BEXUS environment.
    \item[D.04] The absolute position of the telescope relative to the gondola shall be known with a accuracy of 0.1\,degrees.
	\item[D.05] The supporting structure shall not twist by more than 0.1\,degrees.
	\item[D.06] The telescope shall not be pointed within 27\,degrees of the sun.
	\item[D.07] The experiment shall be able to fly during day and night.
	\item[D.08] The temperature of the NIR camera shall be held at 0\,$\pm$5\,$^\circ$C.
	\item[D.09] The images obtained shall be sent to a ground station by the E-link system with a maximum data rate of 1000\,kilo bits per second.
	\item[D.10] The experiment shall be mounted at the side of the gondola.
	\item[D.11] The experiment shall not consume more power than 250\,Wh.
    \item[D.12] The volume of the experiment shall not exceed \SI{0.11}{cm\cubed}.
    \item[D.13] The mass of the experiment shall not exceed 20\,kg.
    \item[D.14] The experiment shall be able to run for at least 2.5\,hours.
    \item [D.15] The experiment should be able to run for at least 4 hours
    \item[D.16] The experiment shall be able to function autonomously.
    \item[D.17] The data stored in the experiment shall be able to survive the landing.
\end{enumerate}
