% https://www.tablesgenerator.com/ highly recommended.

\makeatletter
\renewcommand\@makefntext[1]{\leftskip=3em\hskip-1em\@makefnmark#1}
\makeatother

\begin{longtable}[]{|m{0.06\textwidth}| m{0.48\textwidth} |m{0.13\textwidth} |m{0.1\textwidth}|m{0.15\textwidth}|}

\hline
\textbf{ID} & \textbf{Written requirement} & \textbf{Verification} & \textbf{Test number} & \textbf{Status} \\\hline
F.1 & The telescope shall successfully track the celestial bodies of interest. 
& & & \\\hline

F.2 & The camera shall take images in the near infrared (NIR) spectrum.
& & & \\\hline

P.1 & The gimbal stabilization system shall point the telescope towards the celestial body with an accuracy of at least 1 arc seconds.
& & & \\\hline

P.2 & The optics shall be cable of making pictures of 0.5-1.5 x 0.3-1\,degrees.
& & & \\\hline

P.3 & The NIR camera shall make images in the range of 720-850 to 1200\,nm.
& & & \\\hline

P.4 & The NIR camera shall have a resolution of at least 16\,MP.
& & & \\\hline

P.5 & The NIR camera shall be able to make images with exposure times between 0.5 and 150\,seconds.
& & & \\\hline

P.6 & The experiment shall measure the location and orientation of the gondola.
& & & \\\hline

D.01 & The experiment shall be able to operate in the temperature profile of the BEXUS environment.
& & & \\\hline

D.02 & The experiment shall be able to operate in the pressure profile of the BEXUS environment.
& & & \\\hline

D.03 & The experiment shall be able to operate in the vibration profile of the BEXUS environment.
& & & \\\hline

D.04 & The absolute position of the telescope relative to the gondola shall be known with a accuracy of 0.1\,degrees.
& & & \\\hline

D.05 & The supporting structure shall not twist by more than 0.1\,degrees.
& & & \\\hline

D.06 & The experiment shall never be pointed directly at the sun $\pm$ 27\,degrees.
& & & \\\hline

D.07 & The experiment shall be able to fly during the entire day.
& & & \\\hline

D.08 & The temperature of the NIR camera shall be held at 0\,$\pm$5\,$^\circ$C.
& & & \\\hline

D.09 & The images obtained shall be send to a ground station by the E-link system with a maximum data rate of 1000\,kilo bits per second.
& & & \\\hline

D.10 & The experiment shall be mounted at the side of the gondola.
& & & \\\hline

D.11 & The experiment shall not consume more power than 250\,Wh.
& & & \\\hline

D.12 & The volume of the experiment shall not exceed 65 x 40 x 40\,cm.
& & & \\\hline

D.13 & The mass of the experiment shall not exceed 20\,kg.
& & & \\\hline

D.14 & The experiment shall be able to run for at least 3\,hours.
& & & \\\hline

D.15 & The experiment shall be able to function autonomously.
& & & \\\hline

O.1 & The experiment shall be able to be controlled by the ground station when requested.
& & & \\\hline

O.2 & The experiment shall rotate to a 'safe' location while descending.
& & & \\\hline

\caption{Verification Matrix.}
\label{tab:var-mat}
\end{longtable}
\raggedbottom